Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-08-18 rebuttal.tex

\item \emph{``In this paper, we use locally distributed to indicate that data/compute resides on multiple nodes within one data center. Geographically distributed describes the distribution of data and/or compute across multiple data centers'' Given the above, I think it would be better in this definition to also separate out data creation location from compute location. Intro: Define precisely what is meant by ``dynamic,'' here as it is key to the paper but isn't well defined in Section 1 (see recommendation above to fix this by moving definitions from Section 3).}

\textbf{Response:}

\katznote{attention needed here re distributed and dynamic part of comment}

\nchnote{Partial response:} We have added a summary description of what we mean by distributed and dynamic at the start of Section 2 to reflect the fact that definition of the terminology arose and was refined by the discussions at the workshops, and the analysis of the application scenarios presented.

\katznote{partial response:} In addition, recognizing that the two reviewers have different styles of reading
and different areas of expertise (as do we as authors), we have added a paragraph at the end
of Section 1 to explain how different types of readers might want to approach this paper.  We do
not believe that there is one single way of organizing it that would satisfy all readers.  We have also
added a longer description of each section at this same place.  Also, see our response to point 10 below.

### 2016-08-20 3dpas_intro.tex
minor tweek to abstract

\begin{abstract}
  A common feature across many science and engineering applications is the
  amount and diversity of data and computation that must be integrated to yield
  insights. Data sets are growing larger and becoming distributed; and their
  location, availability and properties are often time-dependent. Collectively, these
  characteristics give rise to dynamic distributed data intensive
  applications. While ``static'' data application have received significant
  attention, the characteristics, requirements, and software systems for the
  analysis of large volumes of dynamic, distributed, and data intensive applications have
  received relatively less attention. This paper surveys several representative dynamic
  distributed data-intensive application scenarios, provides a common conceptual
  framework to understand them, and examines the infrastructure used in support
  of applications.

>>>>

\begin{abstract}
  A common feature across many science and engineering applications is the
  amount and diversity of data and computation that must be integrated to yield
  insights. Data sets are growing larger and becoming distributed; and their
  location, availability and properties are often time-dependent. Collectively, these
  characteristics give rise to dynamic distributed data intensive
  applications. While ``static'' data applications have received significant
  attention, the characteristics, requirements, and software systems for the
  analysis of large volumes of dynamic, distributed data, and data-intensive applications have
  received relatively less attention. This paper surveys several representative dynamic
  distributed data-intensive application scenarios, provides a common conceptual
  framework to understand them, and examines the infrastructure used in support
  of applications.
